---
title: "Filtering Walkthrough"
editor: visual
---

When you are trying to sort and filter out certain works and information, it is important to know which exact functions you should use in order to ensure that you get the information that you're looking for. I will walk you through the steps to sort out information from a data set by using the filter function. 

First we will be using Georgia's voting data from 2016:

Use the function head() to load in the data and give you a snapshot of what the data looks like:
```{r}
head(GA_votedemos_2016_gen)
```
So now we have our data loaded in. But lets say I only want information from the general elections
```{r}
filter(GA_votedemos_2016_gen, elextype == "general")
```
Now that we have all the information from the general elections, then I may want to filter this even more to be more specific. Lets say out of this data set I only want to know about Banks County. I would use %>% to connect my two functions and filter out of the data I just filtered. 
```{r}
filter(GA_votedemos_2016_gen, elextype == "general") %>%
filter(county == "BANKS")

```

