title: "Analysis Walkthrough Example"
author: "Zazni Vlijter"
format:
  html:
    self-contained: true
    code-fold: true
    code-tools: true
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)


```

# Load the datasets

# Exercises

1)  

Join together the election results and urban/suburban/rural tables above, and then use the merged table to:

-   filter for just Virginia

-   group_by and summarize to calculate the mean pct of Trump 2020 vote (`pct_r_2020`) by urban/rural categories (`rural_urban`)

```{r}
full_join(counties_elexresults,counties_rural_urban_suburban)%>%
filter(state_code == "VA")%>% 
group_by(rural_urban)%>%
summarise(averagevotes = mean(pct_r_2020))
```

2)  

Using the joined election results / urban/suburban/rural table created above:

-   filter for just Virginia

-   count up how many counties were won by party in 2020 (`winner_2020`) by urban/rural categories

```{r}
full_join(counties_elexresults, counties_rural_urban_suburban)%>%
filter(state_code == "VA")%>% 
group_by(rural_urban)%>%
count(winner_2020)



```

3)  

Join together the election results and demographics tables above, and then use the joined table to:

-   filter for just Florida

-   group/summarize to calculate the mean pct of Trump 2020 vote in the counties above or below national average for college graduates (`pct_ed_college_all_abovebelow_natl`)

```{r}
inner_join(counties_demographics, counties_elexresults)%>%
filter(state_code == "FL")%>%
group_by(pct_ed_college_all_abovebelow_natl)%>%
summarize(averagevotes = mean(pct_r_2020))

  
  




```

4)  

Using the joined table you made above:

-   group/summarize to calculate the mean pct of Trump 2020 vote by counties above or below the national average for college graduates (`pct_ed_college_all_abovebelow_natl`).

    Note we're looking for the entire country here.

```{r}
inner_join(counties_demographics, counties_elexresults)%>%
group_by(pct_ed_college_all_abovebelow_natl)%>%
summarize(averagevotes = mean(pct_r_2020))



```

Now using the joined datasets above, come up with two groupings you find interesting or newsworthy in a particular state, and replicate the steps above them them instead.

5)  

```{r}
inner_join(counties_demographics, counties_elexresults)%>%
group_by(pct_mil_veteran)%>%
summarize(averagevotes = mean(pct_r_2020))



```

6)  

```{r}
inner_join(counties_demographics, counties_elexresults)%>%
group_by(pct_ed_college_all)%>%
summarize(averagevotes = mean(pct_r_2020))




```

7)  Extra credit

Up until now we've joined two tables together. But we actually have three tables in this project. How might we join all three together into a single table, so all the measures for each county are combined in one place? (Hint: you can do this is multiple steps, doesn't have to be one step only.)

```{r}

full_join(counties_elexresults, counties_rural_urban_suburban)%>% full_join(counties_demographics)




```
